Proposal to improve BBC Search through the use of Linked Data

### 2014-05-17 chapter5.3.tex
Sort of finished chapter 5!

The ``Results Page'' subteam can thus focus on initiating
several iterations of user experience design, user testing
and development of the results page and it is expected this
feature will continue to develop in the background as
other features are worked on by other subteams. It is likely
individual stories might add to the domain model even
to make this simple, responsive rebuild of the results page.

@@

@@

def ingest_jsonld(jsonld_string):
  body = {'jsonld': json.loads(jsonld_string)}
  ElasticSearch().index(index='search', body=body, doc_type='item')
\label{lst:ingest}
\end{lstlisting}

@@

% PICR

@@

% Expiry of content - recrawl/refetch

@@

% Editor's Choice - Triplestore
% Can start to curate other things ahead of time
% Publishing tool?

@@

% CBBC, K&L

@@

% More rich snippets

>>>>

There are modelling decisions still to be
made around whether to use this new vocabulary exclusively
or attempt to follow an existing one such as Schema.org. The
World Wide Web Consortium (W3C) usually recommends the practice
of \emph{extending} existing vocabularies over coining new
ones, but the linked data model always allows us to publish
mappings to existing vocabularies. However, small, bespoke
ontologies are arguably easier to define, control and iterate
in an agile manner and mappings to existing vocabularies
can be published later.

For the rest of this implementation plan, it is assumed
the custom ontology described will be used as replacing it
with equivalent properties from an existing ontology
is not a difficult task at the point of implementation.

Once the model is decided,
the ``Results Page'' subteam can thus focus on initiating
several iterations of user experience design, user testing
and development of the results page and it is expected this
feature will continue to develop in the background as
other features are worked on by other subteams. It is likely
individual stories might add to the domain model even
to make this simple, responsive rebuild of the results page.

@@

This feature involves replacing all programmes entries in
the search indexes with linked data sent through the proposed
indexing chain. The effect for the front end application
will be to unify the three separate categories for
programmes content mentioned in section~\ref{sec:search-results-page}.

In the initial iteration, this will take the form of a single
``Programmes'' category that simply links to microsites
for different programme entities. Direct linking to iPlayer
will be lost temporarily, but restored in the next
feature. Note that users will always be able to reach
iPlayer via programmes microsites.

@@

def ingest_jsonld(jsonld_string):
  body = {'jsonld': json.loads(jsonld_string)}
  ElasticSearch().index(
    index='search', body=body, doc_type='item')
\label{lst:ingest}
\end{lstlisting}

@@

The \emph{Discovery} subteam will need to investigate
suitable mechanisms for notifying when certain programmes
objects have changed. There are asynchronous, message-based
systems in place witin the BBC specifically around
programmes change notifications and the engineered solution
is likely to make use of that.

Alongside this work, those responsible for enrichment and
inference will need to define (and apply) the rules for
mapping the vocabularies used by programmes microsites
to the ontology and vocabulary used in the search application.
Such rules will extend the form introduced in
section~\ref{sec:ld-indexing}.

@@

In this feature, direct links to iPlayer are added back into
search results for programmes.

One difficulty is around
the temporal nature of programmes information. The graph
shown back in figure~\ref{question-time} shows
the time of the next broadcast, but that information will
soon expire and the search system might be interested in
reindexing that programme when the nature of its availability
on BBC iPlayer changes.

It is thus likely that the Discovery subteam working on the
URLNotification component will need to develop components
that query an archive of the linked data ingested to look
for items that may need reingested. They may need to
place requirements on the Ingest team to store an archive
of the linked data within a \emph{triple store} or other
data store (note that Elasticsearch has been known to be
suitable to act as both a search service and a NoSQL-style
document store in one). It is then a decision for teh
engineers as to whether complex SPARQL queries can mine
for programmes (or indeed any) content that has passed
a significant point of time at which the information becomes
out of date or whether to augment the simple ontology
in figure~\ref{fig:basic-ontology} with the concept of
a search result's information \emph{expiring} as shown in
figure~\ref{fig:expiring-ontology}.

\begin{figure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{expiring-ontology.dot}
    \end{dot2tex}
  \end{center}
  \caption{Concept of a potential search result's information expiring has been added}
  \label{fig:expiring-ontology}
\end{figure}

This expiry concept is not necessarily that the content item
should no longer appear in the search indexes, but that the
information should be considered stale and refetching the data
is recommended. This is not too far removed from Google
recrawling pages based on some assessment of how often the page
should be checked, but here we can use the semantic metadata
available publicly (and indeed internally) to get a more
precise idea of a good expiry date.

At this stage, it could
be proposed to send a notification to the URLNotification
component a short time after the date and time within the
value of \emph{any}
\texttt{http://schema.org/endDate} property has passed. A more
suitable strategy might emerge as the individual user stories
within this feature are planned out by the development team.

@@

The current Editor's Choice feature links to the top-level
brand microsite (e.g. the home page for \emph{Question Time})
for any programme, but generally does not link to the pages
for specific series/seasons nor individual episodes. This gives
rise to that idea that something modelled as a potential
search result in our domain model \emph{may} be a recommended
result, but not all results have this property. This can
lead to the next iteration of the domain model/ontology in
figure~\ref{fig:recommended-ontology}, which introduces a
property that indicates when a \texttt{:SearchResult}
can be said to represent a recommended page for any concept.
For instance, the URI for Question Time as a concept
will have the recommended page of the microsite about that
programme.

\begin{figure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{recommended-ontology.dot}
    \end{dot2tex}
  \end{center}
  \caption{Ontology augmented with the concept of a recommended link for an entity}
  \label{fig:recommended-ontology}
\end{figure}

The Ingest subteam should then look at maintaining a second
index of just the names/titles of potential search results
that are marked as ones that might be recommended. The
results page front end subteam can then focus on being
able to query both this new index and the index of documents
so as to render Editor's Choice and organic search results
links respectively on a single page.

The API through which the front end web application queries for
these recommended links can not only expose these recommendations
as linked data, but also allow an administrative application
to create, maintain and remove recommendations should there
be requirements from editorial staff to be able to do so. In this
case, we should revisit the domain model (i.e. iterate it further)
to distinguish between, say, \texttt{:automaticRecommendedLink}
which prompts editorial staff to create a corresponding
\texttt{:approvedRecommendedLink}. This reflects the typical
workflows in editorial web tools that traditionally store unmoderated,
approved, etc. links, but instead encourages through the use of RDF
to publish this as linked data by default. This again follows the
principles of linked enterprise data laid out in chapter~\ref{stateoftheart}.

The developers working on inference should gather requirements
for inferring recommendations from the upstream RDF graphs,
which in the case of programmes apparently follows from simply
creating a recommendation for any programme brand to its
respective ``home page'' or microsite.

@@

The next feature should address removing configuration for
some actively-maintained BBC sites -- such as CBBC and
Knowledge and Learning -- from the existing web crawler
application and instead push discovered URLs through the new
RDF-based indexing chain. The developers working on discovery
should look to push notifications of new, changed and removed
pages to the URLNotification service, even if they originate
from a web crawler.

The enrichment components could be extended to fetch additional
metadata by integrating against backend services that drive
these sites. Investigations will need to be made around this,
but any new information that can be added will be an improvement
over the current way the sites are simply web crawled and scraped.

It is not expected that the domain model should need to change
significantly, so the ingest and results page applications may not
need specific changes, but it is expected that the presentation
of, e.g. the titles, in the search results for these sites will look
cleaner by properly ascertaining the metadata as opposed to relying
on web scraping to takes things out of HTML tags (e.g. the \texttt{<title>}
tag.

This feature is intentionally not specified with as much detail
as the previous features as agile methodologies usually encourage
making most decisions when closer to implementation of the feature, at
which point there may be a lot more information available.

@@

This is another feature that is not over-specified, but it does
clearly follow from the ability to add BBC iPlayer links to
programmes search results that it should be possible to decorate
those results further with a quick indication of when that
programme is next broadcast on a TV or radio service.

The information should already be present in the RDF graphs being indexed,
so this work is theoretically just focused around those developers
working on the search results web application to generate such
decoration in the presentation layers based on information that is
already present in the search indexes.
